Amendments Summary

### 2025-01-02 Thesis/03-chap3.qmd
fix chap 3.1.2

Given that the input is a single residual plot represented as a fixed-resolution image, we can choose the output from the computer vision model to be either binary (classification) or numeric (regression).

@@

>>>>

Given that the input is a single residual plot represented as a fixed-resolution image, the output of the computer vision model can be designed for various tasks: binary classification, categorical classification with multiple classes, or numeric regression.

@@

For a multi-class outcome, the model could classify images into categories such as "contains outliers" vs. "does not contain outliers" or "is non-linear" vs. "not non-linear," among other diagnostic features. While this approach is appealing in theory, it essentially reverts to the traditional testing framework, where tests focus on detecting specific types of model violations in isolation.

One significant advantage of the lineup protocol for residual diagnostics is its ability to detect multiple model violations simultaneously, provided these violations produce visually distinguishable differences in the plots. In contrast, training a classification model would require explicitly defining and mapping all potential violations of interest, or at least the most common ones, which can be impractical. If the goal is to identify specific cases, conventional statistical tests grounded in regression model assumptions are often more effective. Computer vision models may be less suited to such tasks.

### 2025-01-02 Thesis/amend_v2.qmd
fix chap 3.1.2

One of the key advantages of using the lineup protocol for residual diagnostics is its ability to detect multiple model violations simultaneously, provided those violations produce noticeable differences in the data plots. <!--In contrast, training a model discussed above would require us to explicitly define and map out all possible violations of interest—or at least the common ones we want to address.

Additionally, if the ultimate goal is to distinguish between specific cases (e.g., outliers vs. no outliers, or linear vs. non-linear relationships), conventional statistical tests based on regression model assumptions are often more suitable. Computer vision models may not be the best tools for these tasks. Even if we trained a deep learning model for this purpose, it would still face challenges in terms of confidence assessment. Such a model would typically produce a single probability prediction for each predefined violation, limiting its scope and flexibility.-->

The lineup evaluation described in Section 3.5 remains valuable even in this context. By treating the model output as a statistic and comparing it to outputs generated under null assumptions, it adheres to the principles of visual inference and conventional statistical testing. This approach provides a robust framework for interpreting results and avoids the pitfalls of relying solely on predicted probabilities. **XXX Have you made any modifications in the thesis to make these points so that the reader is not likely to ask the same question as Daniela? If so, this needs to be stated here.**

>>>>

One of the key advantages of using the lineup protocol for residual diagnostics is its ability to detect multiple model violations simultaneously, provided those violations produce noticeable differences in the data plots.

The lineup evaluation described in Section 3.5 remains valuable even in this context. By treating the model output as a statistic and comparing it to outputs generated under null assumptions, it adheres to the principles of visual inference and conventional statistical testing. This approach provides a robust framework for interpreting results and avoids the pitfalls of relying solely on predicted probabilities.

To clarify this, I have added two additional paragraphs in Section 3.2.2.
